Sparse Function Space Representation of Neural Networks for Exploration and Retention

### 2023-05-10 paper/main.tex
Rename figs folder to fig
starting to fill out background

\newcommand{\GP}{\mathcal{GP}}
\newcommand{\KL}[2]{\mathrm{D}_\textrm{KL} \dbar*{#1}{#2}}
\newcommand{\MKzz}{\mbf{K}_{\mbf{z}\mbf{z}}}
\newcommand{\MKxx}{\mbf{K}_{\mbf{x}\mbf{x}}}
\newcommand{\MKzx}{\mbf{K}_{\mbf{z}\mbf{x}}}
\newcommand{\MKxz}{\mbf{K}_{\mbf{x}\mbf{z}}}
\newcommand{\vkzi}{\mbf{k}_{\mbf{z}i}}
\newcommand{\vkzs}{\mbf{k}_{\mbf{z}i}}
\newcommand{\vk}{\mbf{k}}
\newcommand{\MLambda}[0]{\mathbold{\Lambda}}
\definecolor{matplotlib-blue}{HTML}{1f77b4}
\newcommand{\N}{\mathrm{N}}
\newcommand{\myexpect}{\mathbb{E}}

@@

\textbf{Dual GP} Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by changing the complexity from $O(n^3)$ where n is number of data points to $O(m^3)$ where $m \ll n$. The key to the complexity saving is to use a sparse distribution

@@

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Metrics for supervised learning with image data} 
	\label{tbl:imagesuper}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{2pt}
	\setlength{\tblw}{0.14\textwidth}

@@

% \begin{figure}
%   \centering
%   \includegraphics[width=0.5\textwidth, angle=270]{figs/weight-space-to-functio-space.pdf}
%   \caption{}
% \end{figure}

% \begin{figure}
%   \centering
%   \includegraphics[width=0.5\textwidth, trim=0 100 0 10]{figs/cartpole-training-curves.pdf}
%   \caption{}
% \end{figure}

@@

    % Use the subcaption package (= subfigure) for sub-plots, that is
    % plot the separate plots separately in Python
    \begin{subfigure}{.4\textwidth}
        \centering
        \input{./figs/example_fig.tex}
    \end{subfigure}
    \hfill
    \begin{subfigure}{.4\textwidth}
        \centering
        \input{./figs/example_fig.tex}
    \end{subfigure}
    \caption{Foo}
    \label{fig:example}
\end{figure}

>>>>

\newcommand{\GP}{\mathcal{GP}}
\newcommand{\KL}[2]{\mathrm{D}_\textrm{KL} \dbar*{#1}{#2}}
\newcommand{\MKzz}{\mbf{K}_{\mbf{z}\mbf{z}}}
\newcommand{\MKxx}{\mbf{K}_{\mbf{x}\mbf{x}}}
\newcommand{\MKzx}{\mbf{K}_{\mbf{z}\mbf{x}}}
\newcommand{\MKxz}{\mbf{K}_{\mbf{x}\mbf{z}}}
\newcommand{\vkzi}{\mbf{k}_{\mbf{z}i}}
\newcommand{\vkzs}{\mbf{k}_{\mbf{z}i}}
\newcommand{\vk}{\mbf{k}}
\newcommand{\MLambda}[0]{\mathbold{\Lambda}}
\definecolor{matplotlib-blue}{HTML}{1f77b4}
\newcommand{\N}{\mathrm{N}}
%\newcommand{\R}{\mathrm{R}}
\newcommand{\myexpect}{\mathbb{E}}

@@

\textbf{Dual GP} A Gaussian process is a prior over functions $f \sim \GP(0, \kappa)$. The prior is characterized by a covariance kernel function $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors. Once combined with a data set ${\mathcal{D}_n = \{(\vx_i, y_i)\}_{i=1}^n}$ with $n$ examples, each modeled by the likelihood $p(y_i \mid f_i)$ at function $f_i = f(\vx_i)$, we can form a posterior using multivariate conditioning.

Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by changing the complexity from $O(n^3)$ where n is number of data points to $O(m^3)$ with $m$ the number of inducing points, where typically $m \ll n$. The key to the complexity saving is to use a sparse distribution $q(\vu; \vm, \MV)$, where $\vm \in \R^{m}$ and $\MV \in \R^{m \times m}$. The distribution at all over points is then defined as $q_{\vu}(f) = \int p(f \mid \vu) q(\vu) d\vu$.

@@

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Metrics for supervised learning with image data} 
	\label{tbl:imagesuper}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{6pt}
	\setlength{\tblw}{0.2\textwidth}

@@

% \begin{figure}
%   \centering
%   \includegraphics[width=0.5\textwidth, angle=270]{fig/weight-space-to-functio-space.pdf}
%   \caption{}
% \end{figure}

% \begin{figure}
%   \centering
%   \includegraphics[width=0.5\textwidth, trim=0 100 0 10]{fig/cartpole-training-curves.pdf}
%   \caption{}
% \end{figure}

@@

    % Use the subcaption package (= subfigure) for sub-plots, that is
    % plot the separate plots separately in Python
    \begin{subfigure}{.4\textwidth}
        \centering
        \input{./fig/example_fig.tex}
    \end{subfigure}
    \hfill
    \begin{subfigure}{.4\textwidth}
        \centering
        \input{./fig/example_fig.tex}
    \end{subfigure}
    \caption{Foo}
    \label{fig:example}
\end{figure}
